---
title: "InClassExercise2"
author: "Fanglin Liu Irene"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r}
library(dplyr)
d <- vdem_1984_2022_external <- read.csv("~/Documents/GitHub/HKU_POLI3148_23Fall_Demo/_DataPublic_/vdem/1984_2022/vdem_1984_2022_external.csv")
```

## 1. **Coodbook lookup**

### i.

```{r}
names(d)
```

According to the codebook, two indicators are concerned with education quality.

Education 15+ (E) (e_peaveduc)

Educational inequality, Gini (E) (e_peedgini)

### ii. 

```{r}
d |> select(country_name) |> distinct()
d |> select(year) |> distinct()
d |> select(country_name, year) |> distinct()
```

### iii.

**The sources for e_peaveduc:**

Source(s): Clio Infra (clio-infra.eu), drawing on Mitchell (1998a, 1998b, 1998c), United States

Census Bureau (2021), UNESCO, Földvári and van Leeuwen (2014), Leeuwen, van LeeuwenLi, Földvári (2011), Leeuwen, van Leeuwen-Li, Földvári (2012a), Leeuwen, van Leeuwen-Li,

Földvári (2012b), Didenko, Foldvari, van Leeuwen (2012).

**The sources for e_peedgini:**

Source(s): Clio Infra (clio-infra.eu), drawing on Mitchell (1998a, 1998b, 1998c), United States

Census Bureau (2021), UNESCO, Földvári and van Leeuwen (2010a), Leeuwen, van LeeuwenLi, Földvári (2011), Leeuwen, van Leeuwen-Li, Földvári (2012a), Leeuwen, van Leeuwen-Li,

Földvári (2012b), Didenko, Foldvari, van Leeuwen (2012)

Link for Clio Infra:

URL: <https://www.clio-infra.eu/docs/Educational_Gini.docx>

## 2. **Subset by columns**

### i. 

```{r}
d_edu <- d |> select(country_name, year, e_peaveduc, e_peedgini)
```

### ii. 

```{r}
d_edu <- d_edu |> rename("country" = "country_name", "avgeduyears" = "e_peaveduc", "edu_inequality" = "e_peedgini")
```

## 3. **Subset by rows**

### i. 

```{r}
d_edu |> slice_max(order_by = avgeduyears, n = 5)
```

### ii. 

```{r}
d_edu |> slice_max(order_by = edu_inequality, n = 5)
```

## 4. 

### i. 

```{r}
d_edu <- d_edu |> mutate(edu_quality_missing = as.numeric(is.na(avgeduyears)))
sum(d_edu$edu_quality_missing)
d_edu_avl <- d_edu |> filter(edu_quality_missing == "0")
d_edu_avl|> group_by(country, year)
```

Therefore there are 1174 country-years where the education quality data are missing.

### ii.

```{r}
mean(d_edu_avl$avgeduyears)
max(d_edu_avl$avgeduyears) - min(d_edu_avl$avgeduyears)
```

### iii.

```{r}
d_edu_avl <- d_edu_avl |> group_by(country) |> mutate(edumean = mean(avgeduyears)) |> ungroup() 
d_edu_avl |> slice_max(order_by = edumean, n = 1)
d_edu_avl |> slice_min(order_by = edumean, n = 1)
```

As the output indicates, Germany performed best with an average education years of 12.93987, while Burkina Faso performs worst with an average education years of 0.9819231
